Included Summary (teaching-v1.0)

### 2020-12-14 experiment-1/analysis/preprocessor/included_summary.Rmd
update included_summary
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("here")) {install.packages("here"); require("here")}

# set working directory
here::i_am("included_summary.Rmd")

# read txt files
dt_ioi <- fread(file = here("trimmed", "data_ioi_1.txt"), sep = ",")
dt_kot <- fread(file = here("trimmed", "data_kot.txt"), sep = ",")
dt_vel <- fread(file = here("trimmed", "data_vel.txt"), sep = ",")
dt_vel_diff <- fread(file = here("trimmed", "data_vel_diff.txt"), sep = ",")
```

@@

### IOIs (Summary)
```{r ioi-summary, echo = FALSE}
dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill)]
```
- SubNr 1 is excluded from data analysis because most of the responses were excluded due to outliers.

@@

## Excluded participnats
- SubNr 1: Most of responses (more than 90%) were removed due to outliers
- SubNr 3: Experimental error
- SubNr 8: Experimental error
- SubNr 14: Experimental error
- SubNr 16: A deviated tempo

>>>>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}

# read txt files
dt_ioi <- fread(file = "./trimmed/data_ioi_1.txt", sep = ",")
dt_kot <- fread(file = "./trimmed/data_kot.txt", sep = ",")
dt_vel <- fread(file = "./trimmed/data_vel.txt", sep = ",")
dt_vel_diff <- fread(file = "./trimmed/data_vel_diff.txt", sep = ",")
```

@@

### IOIs (Summary)
```{r ioi-summary, echo = FALSE}
dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill)]
```

@@

## Excluded participnats
- SubNr 1: A deviated tempo
- SubNr 3: Experimental error
- SubNr 8: Experimental error
- SubNr 14: Experimental error
- SubNr 16: A deviated tempo
